---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# arabic2kansuji

<!-- badges: start -->
<!-- badges: end -->

This `{arabic2kansuji}` is a package consisting of functions to convert Arabic numerals to kansuji.

## Installation

You can install `{arabic2kansuji}` from GitHub:

``` r
devtools::install_github("indenkun\arabic2kansuji")
```

## Example

load library.

```{r example}
library(arabic2kansuji)
```

### `arabic2kansuji`

`arabic2kansuji` is a function that converts Arabic numerals to kansuji verbatim.

There is no need to enclose only half-width Arabic numerals with double-cotation marks.

```{r}
arabic2kansuji(1234567890)
```

If you give a string containing Arabic numerals, everything else is retained except the Arabic numerals to be converted. Strings containing Arabic numerals can be converted, but please enclose them in double-cotations

```{r}
arabic2kansuji("昭和64年は1989年1月7日までです。")
```

By default, it converts only half-width Arabic numerals, but you can also convert only full-width Arabic numerals or convert both full-width and half-width Arabic numerals to kansuji by specifying arguments.

```{r}
# By default, full-width Arabic numerals will not be converted.
arabic2kansuji("東京都新宿区西新宿２丁目８−１")
# It can convert full-width Arabic numerals by providing an argument.
arabic2kansuji("東京都新宿区西新宿２丁目８−１", width = "fullwidth")
arabic2kansuji("全角アラビア数字１２３と半角アラビア数字の混在も引数を指定すると変換できます。", width = "all")
```

By default, 0 is converted to rei (〇), but it can be converted to zero (零) by specifying an argument.

```{r}
arabic2kansuji("令和２年は2020年")
arabic2kansuji("令和2年は2020年", zero = "zero")
```

Since this function only replaces Arabic numerals with kansuji verbatim, it cannot be converted by calculating 1234 as 千二百三十四. This feature is provided by the `arabic2kansuji_num` functions.

### `arabic2kansuji_num`

This `arabic2kansuji_num` calculates and converts a given number to a kanji value. For example, 1234 can be converted to 千二百三十四.

```{r}
arabic2kansuji_num(124271318)
```

However, currently only accept Arabic numerals. It is an issue for the future to support strings containing Arabic numerals and full-width Arabic numerals.

```{r, error=TRUE}
arabic2kansuji_num("124271318人")
```

For more than 17 digits, a warning is given because calculation processing may not be performed correctly due to problems on the R.

```{r}
arabic2kansuji_num(1234567890123456789)
```

Negative values are also supported. The notation will be 負kansuji.

```{r}
arabic2kansuji_num(-123456789)
```

Some values (e.g. 10 to the power of 10, such as 10 to the power of 10) cannot be correctly calculated to a multiple greater than 2147483647, resulting in an error. This is a problem that relies on R's integer processing, so there are no plans to fix it as the present time.

```{r, error=TRUE}
arabic2kansuji_num(10000000000)
```

## Improrts packges

* `{purrr}`
* `{stringr}`
* `{stats}`

## Reference

The code and sites we used to write this code. Thank you very much.

* [Rで文字列中の旧字体を新字体にまとめて変換する - Qiita](https://qiita.com/hzm_0901/items/c77bec84d261e0ae2bfe)
* [uribo/zipangu](https://github.com/uribo/zipangu)

## License

MIT.

## Notice

The email address listed in the DESCRIPTION is a dummy. If you have any questions, please post them on ISSUE.

## Known Issues

* `arabic2kansuji_num` accepts only half-width Arabic numerals and not strings containing Arabic numerals or full-width Arabic numerals.
